DGE's and Enrichment

### 2021-11-15 reports/rmarkdown/manuscript/Figure4-5.Rmd
Add Supp. Tbl 12

@@

>>>>

```{r Suppl. Tbl. 12, include=FALSE}
metadata <- metadata %>% 
  mutate(L_T_groups = paste0(.$Luminal_gr, .$Tissue_gr)) %>%
  mutate(L_T_groups = ifelse(grepl("L2T2|L2T3", .$L_T_groups), .$L_T_groups, NA))

dge_LT <- edgR_dge.fun("L_T_groups", confound=T)
enrich_LT <- db %>%
  map(., ~gene_mod_enrich.fun(dge_LT$top,dge_LT$y,dge_LT$c,
                              db = .x,
                              group_name = "L_T_groups",
                              cuttoff = c(GO=2, KEGG=2) # c(GO=2, KEGG=2.7)
                              ))

#pal <- c("#54ba63","#ad58c6","#d03e7a","#4cb6a9","#bb6fac","#cca442","#8fb53c","#6a7ecd","#63813e","#c46570","#b3743e","#d35238")
#plot_heatmap.fun(enrich_LT, "KEGG", "L_T_groups", "L_T_groups")

t <- dge_LT$top %>% filter(PValue <= 0.01)

df_across <- enframe(list(LtoT=enrich_LT)) %>%  
  unnest_longer(value) %>%
  mutate(res = map(.$value, "res_list")) %>%
  unnest_longer(res) %>%
  mutate(res = map(res, ~rownames_to_column(.x, var = "Terms"))) %>%
  mutate(res = map(res, ~filter(.x, pvalue <= 0.01))) %>%
  group_by(name, value_id) %>%
  mutate(mod = row_number()) %>% ungroup() %>%
  mutate(res = set_names(.$res, paste0(.$value_id,"_gene_module_",.$mod))) %>%
  group_split(name) %>% set_names(., map(., ~unique(.x$name)))

pages <- list(list("DEGs L2T2 vs L2T3"=t), df_across[[1]]$res) %>% flatten()
write.xlsx(pages, file=paste0(out,"Suppl.Tbl.12 L2T2_L2T3_DEGs_and_enrichment.xlsx")) 
```

@@

## igraph network plot
```{r igraph network, echo=FALSE, warning=FALSE} 
# 1. Change the groups of interest by assigning condition_use
# 2. Change the number of genes to be included in the network by changing n       # , results="hold"
#    look at tempD_i and tempU_i to see how many genes was significant
# 3. Adjust the size of the gene nodes and text in the graph by changing; square, circle and txt

# combinations
g <- sheets[-1]

# Set enrichment conditions
n <- 10  # maximum number of TF's to plot
# sizes:
square <- 10
cricle <- 8
txt <- .7

# Create a graph from the list of UP and DOWN regulated genes
i_graph <- function(temp_i, n, square, cricle){
  temp <- lapply( 1:n, function(x){ strsplit(as.character(temp_i$Genes[x]),split = ";")[[1]]  } )
  temp <- map(temp, purrr::discard, is.na) %>% compact() # removes NA
  names(temp) <- temp_i$Term[1:length(temp)]
  temp2 <- lapply( names(temp) , function(x){ rep(x,length(temp[[x]])) })
  temp <- cbind(unlist(temp2),unlist(temp))
  g <- graph_from_data_frame(temp,directed = F)
  v_shape <- ifelse( names(V(g)) %in% unique(temp[,1]) , "square" , "circle" )
  v_color <- ifelse( names(V(g)) %in% unique(temp[,1]) , "honeydew" , "cornsilk" )
  v_size <- ifelse( names(V(g)) %in% unique(temp[,1]) , square , cricle )

  return(list(g=g, v_shape=v_shape, v_color=v_color, v_size=v_size))
  }

# Test parameters
# i <- "TF_PPI_enrichment"
# i <- "TF_TRRUST_enrichment"
# n <- 4
# g <- sheets[-1]
# condition_use <- g[1]
# g <-  g[1]
# temp_i_names <- paste0(strsplit(i, "enrichment"),condition_use,"_UP_", gr_name,".csv") %>% set_names()

# Save all combination plots in one file
save_pdf.fun <- function(i){

  temp_i_names <- grep(gr_name,list.files(paste0(out,i,"/",gr_name),full.names=F),value=T) %>%
    set_names()
  temp_i <- imap(temp_i_names, ~read.csv2(paste0(out,i,"/",gr_name,"/",.x)))
  obj_igraph <- imap(temp_i, ~i_graph(.x, n, square, cricle))
  pattern <-paste(g , collapse="|")

  par(mar = c(0, 0, .7, 0))  #bottom, left, top, right
  p <- imap(obj_igraph,
       ~with(.x, 
               plot.igraph(g, label=V(g), 
               main = paste0(str_extract(.y,pattern)," ",str_extract(.y, "UP|DOWN")," regulated genes"),
               layout=layout_with_kk(g), vertex.label.color="black" ,
               vertex.size=v_size, vertex.label.cex=txt , vertex.label.font=2, 
               vertex.shape=v_shape, vertex.color=v_color, marigin = c(-1,-4,0,0),
               vertex.frame.color="grey60", curved=F) 
  ))
  #text(0,1.15, paste0(str_extract(.y,pattern)," ",str_extract(.y, "UP|DOWN")," regulated genes"), cex=1.2, font=2)
  dev.copy2pdf(file = paste0(out, "Plots/", gr_name, "_network_", i,".pdf", sep=""))
}
